CommonMind Consortium: DLPFC

### 2020-09-22 combined_analysis/diff.networks.Rmd
Update diff networks

df_test_meta = module_meta_analsis( df_test_recal )

@@

# Disease network
## Difference networks
```{r diff.networks.Dx}

resVersion = "Dx"
variable = 'Dx'

diff.net.Dx = get_difference_network(resid.add[[resVersion]], METADATA, variable)

# res = pickSFT( diff.net.Dx )

# Discover clusters in first cohort
#----------------------------------

C = diff.net.Dx[[1]]
C.diff.discovery = C[[2]]^pwr - C[[1]]^pwr
C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]

rm(diff.net.Dx) # saving this to disk is slow, so just delete it

dynamicColors.Dx = labels2colors(dynamicMods )
tab = table(dynamicColors)
hist(tab, xlab="Cluster size")
```

```{r testing.Dx}
# Hypothesis testing     
df_test.Dx = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx, METADATA, variable, useSLED=FALSE)  
```

```{r recalibrate.Dx}
table(df_test.Dx$FDR < 0.05)

df_test_recal = apply_permutation_null( df_test.Dx )

## Discovery cohort
```{r plot.discovery.Dx}
# plot discovery and testing.  
ggplot(df_test.Dx, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test.Dx$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

```{r modules.in.discovery.Dx, fig.width=10, fig.height=50}

figList = lapply(df_test$Module[1:5], function(mod){

	plot_module( mod, df_test.Dx, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt")   
	})

## Replication cohort
```{r second.cohort.Dx, fig.width=6, fig.height=12}
df_cohort2 = df_test.Dx[df_test.Dx$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=100}

i = which(df_cohort2$FDR < 0.05)[1:10]

	plot_module( mod, df_test.Dx, METADATA, dynamicColors.Dx, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
	})

## Module enrichment
```{r top.enrich.Dx}
df_module.Dx = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
						Module = dynamicColors.Dx)

df_module_enrich.Dx = enrich.test( df_module.Dx, go.gs, df_cohort2$Module[i], 150)
```

```{r plot.enrich.Dx, fig.width=9, fig.height=25}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Dx, module, 8) + ggtitle(module)
	})    
plot_grid(plotlist = figList, ncol=1)
```

## DE enrichment
```{r cameraPR.Dx, fig.width=7, fig.height=20}
res_enrich_DE = enrich_module_DE( df_module.Dx )

>>>>

@@

# <!---

# # Disease network
# ## Difference networks
# ```{r diff.networks.Dx}

# # Compute difference networks
# ##############################

# resVersion = "Dx"
# variable = 'Dx'

# diff.net.Dx = get_difference_network(resid.add[[resVersion]], METADATA, variable)

# # res = pickSFT( diff.net.Dx )

# # ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

# # Discover clusters in first cohort
# #----------------------------------

# C = diff.net.Dx[[1]]
# C.diff.discovery = C[[2]]^pwr - C[[1]]^pwr
# C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]

# rm(diff.net.Dx) # saving this to disk is slow, so just delete it

# hcl = hclust( as.dist(C.diff.discovery) )

# # dynamicMods = cutreeDynamic(hcl, distM=C.diff.discovery, minClusterSize = minClusterSize, deepSplit=2)
# dynamicMods = cutree(hcl, k=200)

# dynamicColors.Dx = labels2colors(dynamicMods )
# tab = table(dynamicColors)
# hist(tab, xlab="Cluster size")
# ```

# ```{r testing.Dx}
# # Hypothesis testing     
# df_test.Dx = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx, METADATA, variable, useSLED=FALSE)  
# ```

# ```{r recalibrate.Dx}
# table(df_test.Dx$FDR < 0.05)

# df_test_recal = apply_permutation_null( df_test.Dx )

# table(df_test_recal$FDR < 0.05)

# df_test_meta = module_meta_analysis( df_test_recal )

# table(df_test_meta$FDR < 0.05)
# ```

# ## Discovery cohort
# ```{r plot.discovery.Dx}
# # plot discovery and testing.  
# ggplot(df_test.Dx, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test.Dx$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
# ```

# ```{r modules.in.discovery.Dx, fig.width=10, fig.height=50}

# figList = lapply(df_test$Module[1:5], function(mod){

# 	plot_module( mod, df_test.Dx, METADATA, dynamicColors, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt")   
# 	})

# plot_grid( plotlist = figList, ncol=1)
# ```

# ## Replication cohort
# ```{r second.cohort.Dx, fig.width=6, fig.height=12}
# df_cohort2 = df_test.Dx[df_test.Dx$Cohort == "NIMH-HBCC",]
# df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
# table(df_cohort2$FDR < 0.05)

# df = df_cohort2[df_cohort2$P.Value < 0.1,]

# ggplot(df, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
# ```

# ```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=100}

# i = which(df_cohort2$FDR < 0.05)[1:10]

# figList = lapply(df_cohort2$Module[i], function(mod){

# 	plot_module( mod, df_test.Dx, METADATA, dynamicColors.Dx, C.diff.discovery, resid.add[[resVersion]], variable, "NIMH-HBCC")   
# 	})

# plot_grid( plotlist = figList, ncol=1)
# ```

# ## Module enrichment
# ```{r top.enrich.Dx}
# df_module.Dx = data.frame(	ENSEMBL = rownames(C.diff.discovery) %>% trim_ensembl_ids, 
# 						Module = dynamicColors.Dx)

# df_module_enrich.Dx = enrich.test( df_module.Dx, go.gs, df_cohort2$Module[i], 150)
# ```

# ```{r plot.enrich.Dx, fig.width=9, fig.height=25}
# figList = lapply( df_cohort2$Module[i], function(module){
# 	plot_enrich(df_module_enrich.Dx, module, 8) + ggtitle(module)
# 	})    
# plot_grid(plotlist = figList, ncol=1)
# ```

# ## DE enrichment
# ```{r cameraPR.Dx, fig.width=7, fig.height=20}
# res_enrich_DE = enrich_module_DE( df_module.Dx )

# figList = lapply( df_cohort2$Module[i], function(module){

# 	res = res_enrich_DE[res_enrich_DE$Geneset == module,]

# 	lim = max(-log10(res$PValue))

# 	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0), lim=c(0, lim*1.05)) + ggtitle(module) + geom_hline(yintercept=-log10(0.05), color="red", linetype="dashed")
# }) 
# plot_grid(plotlist = figList, ncol=1)
# ```

# --->
